|

### 2016-05-23 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

@@

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` of NULL/unmapped values.

>>>>

### From Docker 
```{r echo=F}
tmp <- (p3_table[!is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

@@

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from Docker, `r names(bt_tmp)[4:5]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` of NULL/unmapped values.
